My title

### 2024-03-11 paper/paper.qmd
changes

-------------------------------needs some explanation
```{r}
# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.

@@

# generate predictions for each of our grouped cells
props$estimate <- predict.glm(political_preferences1, newdata = props,
                          type = "response")

# create a new column with number of voters from each cell voting Biden
props <- props %>% mutate(num_voters = n*estimate)

# get errors for our prediction
errors <- predict.glm(model, newdata = props,
                      type = "response", se.fit = T)
lower <- errors$fit - errors$se.fit
upper <- errors$fit + errors$se.fit

# combine the proportions and the errors we generated
props_error <- cbind(props, lower, upper)
props_error <- props_error %>% 
  rename("lower" = ...11,
         "upper" = ...12)

# create a new column with number of voters from each cell voting Biden
props_error <- props_error %>% mutate(num_voters_lower = n*lower,
                                num_voters_upper = n*upper)

# create a new dataset which contains upper and lower estimates for proportions
# of votes for each state
voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
                                       biden_predict_prop_lower = lower*prop,
                                       biden_predict_prop_upper = upper*prop) %>%
  group_by(stateicp) %>%
  summarise(biden_predict = sum(biden_predict_prop),
            biden_predict_lower = sum(biden_predict_prop_lower),
            biden_predict_upper = sum(biden_predict_prop_upper))
```

```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
# get state by state proportions for our polling data
polling_props <- polling %>% 
  group_by(stateicp, vote_biden) %>% 
  summarise(n = n()) %>% 
  mutate(prop = n/sum(n))

# combine the polling data proportions with the post-stratification data
poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
poll_post_biden <- poll_post_biden %>% 
  filter(vote_biden == 1)

# plot for predictions

poll_post_biden %>% 
  ggplot(aes(x = employ, y = biden_predict)) +
  geom_point(aes(color = "black")) +
  geom_line(aes(group = 1)) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
  geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
              alpha = 0.2, fill = "red") +
  geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
            linetype = "twodash") +
  geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
  geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
  scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
  labs(title = "Proportion of People voting for Joe Biden by State",
       x = "State", y = "Percentage Voting Biden")
```

@@

# Marginal Effect 
political_preferences_predictions <- predictions(political_preferences1) |>
  as_tibble()

political_preferences_predictions

@@

```{r}
library(margins)

# Marginal effects for each predictor variable
marginal_effects <- margins(political_preferences1)

# Plotting marginal effects for race
race_effects <- dyplot(marginal_effects, variables = "race")
race_effects

# Plotting marginal effects for region
region_effects <- dyplot(marginal_effects, variables = "region")
region_effects

# Plotting marginal effects for employ
employ_effects <- dyplot(marginal_effects, variables = "employ")
employ_effects

@@

```{r}
# Load required libraries
library(bayestestR)

# Extract posterior draws from the model object
posterior_draws <- as.matrix(political_preferences1)

# Define the predictor variables for which you want to compute marginal effects
predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
                         "Other race", "Two or more races", "White", "Northeast", 
                         "South", "West", "Homemaker", "Other employment", 
                         "Part-time", "Permanently disabled", "Retired", 
                         "Student", "Temporarily laid off", "Unemployed")

# Compute marginal effects
marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)

# Summary of marginal effects
summary(marginal_effects)

@@

```{r}
library(tidybayes)

# Extract draws from the Bayesian model
draws <- spread_draws(political_preferences1)

# Plot the posterior distribution of a predictor variable
ggplot(draws, aes(x = raceBlack)) +
  geom_density(fill = "skyblue", color = "black") +
  labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-modelresults1
#| fig-cap: "Credible intervals for predictors of support for Biden 1"
# Create the model plot
model_plot <- modelplot(political_preferences1, conf_level = 0.9)

@@

## Second discussion point

@@

## Talk about mail-in ballots AND Trump's later reaction to losing

>>>>

-------------------------------needs some explanation
```{r}
# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.
political_preferences1 <-
  readRDS(file = here::here("models/political_preferences1.rds"))

@@

# # generate predictions for each of our grouped cells
# props$estimate <- predict.glm(political_preferences1, newdata = props,
#                           type = "response")
# 
# # create a new column with number of voters from each cell voting Biden
# props <- props %>% mutate(num_voters = n*estimate)
# 
# # get errors for our prediction
# errors <- predict.glm(model, newdata = props,
#                       type = "response", se.fit = T)
# lower <- errors$fit - errors$se.fit
# upper <- errors$fit + errors$se.fit
# 
# 
# # combine the proportions and the errors we generated
# props_error <- cbind(props, lower, upper)
# props_error <- props_error %>% 
#   rename("lower" = ...11,
#          "upper" = ...12)
# 
# # create a new column with number of voters from each cell voting Biden
# props_error <- props_error %>% mutate(num_voters_lower = n*lower,
#                                 num_voters_upper = n*upper)
# 
# # create a new dataset which contains upper and lower estimates for proportions
# # of votes for each state
# voting_biden <- props_error %>% mutate(biden_predict_prop=estimate*prop,
#                                        biden_predict_prop_lower = lower*prop,
#                                        biden_predict_prop_upper = upper*prop) %>%
#   group_by(stateicp) %>%
#   summarise(biden_predict = sum(biden_predict_prop),
#             biden_predict_lower = sum(biden_predict_prop_lower),
#             biden_predict_upper = sum(biden_predict_prop_upper))
```

```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
# # get state by state proportions for our polling data
# polling_props <- polling %>% 
#   group_by(stateicp, vote_biden) %>% 
#   summarise(n = n()) %>% 
#   mutate(prop = n/sum(n)) 
# 
# # combine the polling data proportions with the post-stratification data
# poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
# poll_post_biden <- poll_post_biden %>% 
#   filter(vote_biden == 1)
# 
# # plot for predictions
# 
# poll_post_biden %>% 
#   ggplot(aes(x = employ, y = biden_predict)) +
#   geom_point(aes(color = "black")) +
#   geom_line(aes(group = 1)) +
#   scale_y_continuous(labels = scales::percent) +
#   theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
#   geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
#               alpha = 0.2, fill = "red") +
#   geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
#             linetype = "twodash") +
#   geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
#   geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
#   scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
#   labs(title = "Proportion of People voting for Joe Biden by State",
#        x = "State", y = "Percentage Voting Biden")
```

@@

# # Marginal Effect 
# political_preferences_predictions <- predictions(political_preferences1) |>
#   as_tibble()
# 
# political_preferences_predictions

@@

```{r}
# library(margins)
# 
# # Marginal effects for each predictor variable
# marginal_effects <- margins(political_preferences1)
# 
# # Plotting marginal effects for race
# race_effects <- dyplot(marginal_effects, variables = "race")
# race_effects
# 
# # Plotting marginal effects for region
# region_effects <- dyplot(marginal_effects, variables = "region")
# region_effects
# 
# # Plotting marginal effects for employ
# employ_effects <- dyplot(marginal_effects, variables = "employ")
# employ_effects

@@

```{r}
# # Load required libraries
# library(bayestestR)
# 
# # Extract posterior draws from the model object
# posterior_draws <- as.matrix(political_preferences1)
# 
# # Define the predictor variables for which you want to compute marginal effects
# predictor_variables <- c("Black", "Hispanic", "Middle Eastern", "Native American", 
#                          "Other race", "Two or more races", "White", "Northeast", 
#                          "South", "West", "Homemaker", "Other employment", 
#                          "Part-time", "Permanently disabled", "Retired", 
#                          "Student", "Temporarily laid off", "Unemployed")
# 
# # Compute marginal effects
# marginal_effects <- marginal_effects(posterior_draws, variables = predictor_variables)
# 
# # Summary of marginal effects
# summary(marginal_effects)

@@

```{r}
# library(tidybayes)
# 
# # Extract draws from the Bayesian model
# draws <- spread_draws(political_preferences1)
# 
# # Plot the posterior distribution of a predictor variable
# ggplot(draws, aes(x = raceBlack)) +
#   geom_density(fill = "skyblue", color = "black") +
#   labs(x = "Black", y = "Density", title = "Posterior Distribution of Black Variable")

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-modelresults2
#| fig-cap: "Credible intervals for predictors of support for Biden 2"
# Create the model plot
model_plot <- modelplot(political_preferences1, conf_level = 0.9)

@@

## Regional Variations

@@

## COVID and Mail-in Ballots

Other than race, region, employment, and other usual socioeconomical factors, the special situation of COVID-19 and mail-in-ballots also heavily contributed to the election turnout, leading to Biden's victory.  Many Republican's shift from Trump to Biden is attributed to Trump's poor COVID responses and policies.

Mail-in-ballots also spanned many controversy over fraud election as Trump claims
